### 2018-07-13 paper/message-passing-design.tex
Sphinxes: adds CreateReply, UseReply, CreateFwd
Sphinxes: minor edits

We now describe a protocol \ac{SPOR}, which uses the \ac{POR} of Sphinxes to 
transfer large messages from a source to a destination.
We provide the following algorithms:
\begin{itemize}
  \item \(\SPOR[\Send]\) (\cref{SPORSend}).
  \item \(\SPOR[\Fwd]\) (\cref{SPORFwd}).
  \item \(\SPOR[\Recv]\) (\cref{SPORRecv}).
\end{itemize}

Say that Alice wants to send a message \(m\) to Bob.
Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
algorithm.
Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateReply\) and 
gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
At a later point, Alice attaches a message \(m\) to the reply header (using 
\(\AttachPayload\), creates a forward header using \(\CreateFwd\) and attaches 
the reply header as payload (\(\AttachPayload\)) to the forward header.
Then she send this packet to the first node, \ie invokes the \(\SPOR[\Fwd]\) 
algorithm on the first node.
The node will then process the header and in turn forward the packet to the 
next node.
When a node receives a packet where the nodes of the next layer is 
\(\{\rdvnode\}\), it will parse they payload as a packet to be forwarded.
When a node receives a packet where the nodes of the next layer is 
\(\{\nullnode\}\), then it knows that it is the intended recipient.

>>>>

We now describe a protocol \ac{SPOR}, which uses Sphinxes to transfer large 
messages from a source to a destination.
We provide the following algorithms:
\begin{itemize}
  \item \(\SPOR[\Send]\) (\cref{SPORSend}).
  \item \(\SPOR[\Fwd]\) (\cref{SPORFwd}).
  \item \(\SPOR[\Recv]\) (\cref{SPORRecv}).
\end{itemize}

Say that Alice wants to send a message \(m\) to Bob.
Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
algorithm.
Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateReply\) and 
gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
At a later point, Alice attaches a message \(m\) to the reply header (using 
\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
reply header as payload.
Then she send this packet to the first node, \ie invokes the \(\SPOR[\Fwd]\) 
algorithm on the first node.
The node will then process the header and in turn forward the packet to the 
next node.
When a node receives a packet where the nodes of the next layer is 
\(\{\rdvnode\}\), it will parse they payload as a packet to be forwarded.
When a node receives a packet where the nodes of the next layer is 
\(\{\nullnode\}\), then it knows that it is the intended recipient.
